An Automatic Verification Framework for Software Configurations

### 2016-05-09 OSDI/check.tex
config: updated

With the learned rules and constraints in hand,
\app checks whether any entry in a target configuration file
violates the learned rules.
For a given configuration file, \app parses it using the same
way employed in the translator, thus obtaining a structured
and typed representation for the target configuration file.
Then, the checker uses two sub-modules to check the
following aspects of the target configuration file.

>>>>

With the learned rules and constraints in hand (generated
by the learner module),
\app checks whether any entry in a target configuration file
violates the learned rules and constraints.
For a given configuration file, \app parses it using the same
way employed in the translator, thus obtaining a structured
and typed representation for the target configuration file.
Then, the checker uses two sub-modules to check the
following aspects of the target configuration file.

\para{Entry missing violation.}
\app 's checker can detect whether two or more entries should
appear together in the same configuration file based upon
entry missing rules generated by the learner.

### 2016-05-09 OSDI/motiv.tex
config: updated

\para{Example~1: Ordering errors.} 
The first class of configuration errors we handle was first reported by 
Yin {\em et al.}~\cite{yin11anempirical}.
For instance, when a user configures PHP to run with the
Apache HTTP Server, this user might write, amongst others, 
the following lines in the configuration file.

@@

\para{Example~2: Fine-grained value correlation errors.} 
In a real-world misconfiguration example~\cite{correlation}, 
a user configures his MySQL as the following.

@@

\para{Example~3: Entry missing errors.} 
Many critical system outages result from the fact that an important
entry was missing in the configuration file. 
We call such a problem an {\em entry missing error}.
In a public misconfiguration dataset~\cite{configdataset},
many MySQL failure reports were caused by
missing entry errors.
Below is a real-world entry missing error example~\cite{yin11anempirical}:
when a user wants to use OpenLDAP to enable her directory access
protocol, she needs to use the password policy overlay. This is usually
achieved via the following entries in the OpenLDAP configuration file:

>>>>

\para{Example~1: Ordering error.} 
The first class of configuration errors we handle was first reported by 
Yin {\em et al.}~\cite{yin11anempirical}.
For instance, when a user configures PHP to run with the
Apache HTTP Server, this user might write, amongst others, 
the following lines in the configuration file.

@@

\para{Example~2: Fine-grained value correlation error.} 
In a real-world misconfiguration example~\cite{correlation}, 
a user configures his MySQL as the following.

@@

\para{Example~3: Entry missing error.} 
Many critical system outages result from the fact that an important
entry was missing in the configuration file. 
We call such a problem an {\em entry missing error}.
In a public misconfiguration dataset~\cite{configdataset},
many MySQL failure reports were caused by
missing entry errors.
Below is a real-world entry missing error example~\cite{yin11anempirical}:
when a user wants to use OpenLDAP to enable her directory access
protocol, she needs to use the password policy overlay. This is usually
achieved via the following entries in the OpenLDAP configuration file:
